Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-11 WSSSPE3/report/wg_appendix_funding_spec_expert.tex
very small edits to edits to edits to edits
Appendix H:  one-character change.
Changes to fix "Choinotes"

\begin{itemize}
\item Lorraine Hwang -- UC Davis
\item Simon Trigger \choinote{TBD}
\item Nancy Wilkins-Diehr -- San Diego Supercomputer Center
\item Alexander Vyushkov -- University of Notre Dame
\item Sandra Gesing -- University of Notre Dame
\item Ali Swanson -- University of Oxford

@@

The UK allows this kind of collaboration to support the creation of scientific
software for the large supercomputing resource (ARCHER). However, while the
support can come from the staff of the Edinburgh Parallel Computing Centre,
who hosts the computer, this ``embedded CSE'' resource also funds the
programming coming from local groups. This has been very helpful in providing
funding to establish local groups. It works best when these groups develop good
collaborations with national cyberinfrastructure pools. When an organization
assembles a developer pool, diversity is developed and skills can be
transferred.

@@

We will also look for examples of groups which have successfully become self-
sustaining following. \choinote{following what?}

>>>>

\begin{itemize}
\item Lorraine Hwang -- UC Davis
\item Simon Trigger -- BioTeam, Inc.
\item Nancy Wilkins-Diehr -- San Diego Supercomputer Center
\item Alexander Vyushkov -- University of Notre Dame
\item Sandra Gesing -- University of Notre Dame
\item Ali Swanson -- University of Oxford

@@

The UK allows this kind of collaboration to support the creation of scientific
software for the large supercomputing resource (ARCHER). However, while the
support can come from the staff of the Edinburgh Parallel Computing Centre,
who hosts the computer, this ``embedded CSE'' resource also funds the
programming coming from local groups. This has been very helpful in providing
funding to establish local groups. These groups work best when they develop good
collaborations with national cyberinfrastructure pools. When an organization
assembles a developer pool, diversity is developed and skills can be
transferred.

@@

We will also look for examples of groups which have successfully become self-
sustaining following initial seed funding.
